\vspace{5cm} \normalsize \textsc{\NetIDb} \\ [2.0cm] \HRule{0.5pt} \\ \LARGE \textbf{\uppercase{\documenttitle}} \HRule{2pt} \\ [0.5cm] \normalsize \textsc{Sergio Castañeiras Morales\\NIU:1598456\\ }\normalsize \vspace*{5\baselineskip}

### 2025-04-27 Manuscript/Plantilla memòria TFG 2024_25.tex
writting

\setcounter{page}{1}
\pagenumbering{arabic}
\section{Introduction}
The impact of \gls{ai} on science has been nothing short of a groundbreaking revolution, with few comparable precedents. The rapid advancements in \gls{ai} have transformed numerous scientific fields\cite{AlphaFold2BiologyAndMedicine}\cite{NationalLibraryOfMedicineGeneralArticle}, including computational chemistry. Today, one of the primary goals of computational chemistry is to predict the properties of unstudied substances while minimizing experimental costs. Traditional approaches in chemistry often rely on complex laboratory techniques, which, while effective, can be time-consuming, expensive, and resource-intensive. In contrast, computational chemistry offers a wide range of methods capable of predicting a molecule's properties with reasonable accuracy. However, when \gls{ai} comes into play, predictions have demonstrated an almost surgical precision.

Perhaps one of the most representative events showcasing the enormous impact of \gls{ai} on chemistry is the 2024 Nobel Prize in Chemistry. The winners, David Baker\cite{NobelPrizeBale}, along with Demis Hassabis and John Jumper\cite{NobelPrizeJumper}, were not traditionally trained chemists. Instead, their expertise lies in \gls{ai} algorithms and \gls{ml} methods applied to protein research. This milestone, among others, triggered a surge of chemistry researchers diving into the world of \gls{ai}, seeking applications for their respective fields. Today, the thrilling progress in computational chemistry has been further reinforced by these cutting-edge tools\cite{MachineLearningPaper5Lipoxygenase}, and the rapid pace of development keeps the scientific community eagerly anticipating future applications in fields such as medicine, materials science, and beyond. In this project we aim to apply the new \gls{ai} and \gls{ml} algorithms to our object of study, the \gls{ptgs2} also known as \gls{cox2}, a protein tightly linked to the onset of numerous cancers forms\cite{Cox2CancerReview}.

Although significant advancements have been made, cancer still accounts for over 8 million deaths per year worldwide, and the scientific and medical communities remain far from achieving its complete eradication. Inflammation is one of the hallmarks of carcinogenesis; in fact, various cancer therapies target inflammation as a means of preventing and reducing cancer occurrences. When a tissue is damaged, inflammation protects the organism from infections caused by external pathogens, a key function of the immune system to prevent the presence of invaders in the body. During the inflammatory process, cells proliferate under the command of the immune system to replace the damaged cells of the affected tissue. However, if this cell reproduction continues beyond the healing of the damaged tissue, it can potentially lead to cancer, contradicting the initial healing purpose of the inflammatory process. In some cases, inflammation can become chronic, leading to tumor development and uncontrolled cell proliferation. As a result, a wide range of drug prototypes have been designed to suppress inflammation. However, many of these drugs have been linked to severe side effects, including immunosuppression, cardiovascular risks, and gastrointestinal complications. Consequently, the administration of these drugs is often contrindicative, and the search for a more effective and safer treatment remains ongoing. Plently of the research in this field is mainly focused on the pro-inflamatory enzyme \gls{cox2}, one of the main commanders in the inflammation process, subsequently, a therapy based on the he chemical inhibition of the \gls{cox2} with no side effects has been one of the research lines in cancer treatment leading to a considerable amount of experiments and data.

The interest in the \gls{cox2} inhibitors has granted the scientific community with a plethora of molecule's inhibition potentials for this protein. In this project we do focus on the \gls{ic50}.

Currently, the pharmacological therapies for the \gls{cox2} inhibition are based on \gls{nsaid}\cite{nsaidDefinition} such as the popular ibuprofen or aspirin. However they have proved to be related to cardiovascular diseases and are contraindicated for people with more than 50 years or people with gastrointestinal problems, among others. One of the best drug candidates is

\noindent\makebox[\linewidth]{\rule{\paperwidth}{0.4pt}}

\textbf{Dr.Gonzalez and Dr.Lluch project}

The project seeks to advance the understanding and treatment of cancer by approaching it as an inflammation-based disease and developing innovative drug design strategies. Unlike traditional approaches that often rely on broad-spectrum anti-inflammatory drugs, this research aims to create targeted therapies that mitigate or halt the inflammatory processes closely linked to cancer progression. Chronic inflammation is recognized as a key driver of tumor development, promoting immune evasion, genetic mutations, and uncontrolled cell proliferation. However, existing treatments such as nonsteroidal anti-inflammatory drugs (NSAIDs) and COX-2 inhibitors come with significant side effects, including immunosuppression, cardiovascular risks, and gastrointestinal complications, which limit their long-term clinical application.

By adopting an interdisciplinary approach that integrates Theoretical Molecular Biology, Chemistry, Biochemistry, Physics, and Computer Science, this project will explore new molecular strategies for drug design. A major focus will be on targeting key inflammatory enzymes such as COX-2 and lipoxygenases, which are strongly implicated in cancer-related inflammation. Given the research team’s extensive experience in studying these enzymes—demonstrated through 39 published studies—the project aims to leverage Theoretical Chemistry methods, including Quantum Mechanics, Statistical Mechanics, and Biomolecular Simulations, to develop safer and more effective pharmacological interventions.

One of the project’s central hypotheses is that many cancers share a fundamental inflammatory component, making inflammation control a promising therapeutic avenue. The research will investigate novel mechanisms to selectively inhibit or modulate the activity of COX-2 and related enzymes without causing harmful systemic effects. In particular, photopharmacology—using light-activated drug molecules—will be explored as a means of achieving spatial and temporal control over drug activity, potentially reducing off-target effects.

Beyond cancer, the findings from this project could have far-reaching implications for other inflammation-related diseases. Chronic inflammation has been identified as a major underlying factor in conditions such as cardiovascular disease, diabetes, and neurodegenerative disorders like Alzheimer’s. As highlighted by Harvard Medical School, inflammation may be the common link among many of the world’s most prevalent and deadly diseases. By developing new strategies to control inflammation in cancer, this research could also contribute to broader medical advancements, ultimately benefiting patients, healthcare systems, and the pharmaceutical industry.

\noindent\makebox[\linewidth]{\rule{\paperwidth}{0.4pt}}

The impact of \gls{ai} on science has been nothing but an outstanding breakthrough, with few comparable predecessors. The rapid advancements in \gls{ai} have transformed numerous scientific fields\cite{AlphaFold2BiologyAndMedicine}\cite{NationalLibraryOfMedicineGeneralArticle}, including computational chemistry. Nowadays, one of the main goals of computational chemistry is to predict certain properties of unstudied substances with minimal experimental costs\cite{AlphaFold2CommumityAssesment}. Traditional approaches in chemistry often rely on complex laboratory techniques, which, while effective, can be time-consuming, expensive and resource-intensive. On the other hand, \gls{ai} algorithms have already proved exceptional predictive capabilities in countless fields, and computational chemistry is no exception. \gls{ai} provides an alternative by offering highly accurate predictions based on existing data, optimising research processes, and accelerating scientific discovery.\par

This project aims to implement artificial intelligence in computational chemistry, concretely, using AI-based algorithms to predict a drug’s inhibition potential\cite{BookIC50} for a given protein. To achieve this, we make use of the ChEMBL database\cite{ChemblDatabase}, a vast repository of bioactive molecules with drug-like properties. We extract all known molecular data with a documented inhibition potential for the target protein, creating a comprehensive dataset. The chemical descriptors of each molecule in the database are then computed using AlvaDesk\cite{MauriMolecularDescriptorsBook}\cite{AlvaDescSecondPaper} software. Around $10^4$ descriptors are calculated\cite{DescriptorsBookClassification}, which comprehend from the elemental molecular weight to the complex equipotential electronic surface, providing critical information about each compound’s behaviour. The resulting dataset is subsequently used to train \gls{ai} models, enabling them to predict the inhibition potential of unknown compounds. Finally, we evaluate the reliability of each model by testing it against real experimental data. \par

It is important to emphasise the central hypothesis of this project: \emph{There exists a combination (or combinations) of chemical descriptors that are directly correlated with the inhibition of the protein}. While this idea may seem fundamental, it remains unproven due to the complexity of molecular interactions and the vast number of possible descriptor combinations. Despite significant progress in computational chemistry, identifying the exact descriptors that govern inhibition potential has been a persistent challenge. The lack of an ultimate proof underscores the need for advanced computational techniques. By analysing large datasets, \gls{ai} can detect hidden correlations that may not be immediately apparent through traditional statistical methods.\par

At this stage, we focus on \gls{cox2}, a protein well known for its strong association with cancer development and inflammatory diseases\cite{DefinitionCOX2CancerDictionary}. \gls{cox2} plays a crucial role in the biosynthesis of prostaglandins, which mediate inflammation and pain. Overexpression of COX-2 has been linked to various types of cancer, making it a prime target for drug development. \gls{cox2} inhibitors, such as Celecoxib (Def. \ref{definitionCelecoxib}) and Rofecoxib (Def. \ref{definitionRofecoxib}), have been widely studied for their therapeutic potential. The scientific community has devoted an extensive research to \gls{cox2}, even before the rise of \gls{ai}, due to its biomedical significance\cite{Cox2InhibitorsReview}. By applying \gls{ai} models to \gls{cox2}, we assess their compatibility with the latest research findings, demonstrating AI’s potential as a powerful tool in computational chemistry research. Our approach not only validates AI’s effectiveness in predicting inhibition potential but also provides insights into the underlying molecular mechanisms governing COX-2 interactions.\par

The AI algorithm used is a in this study is a \gls{ml} model known as the \gls{rf} algorithm\cite{MachineLearningRandomForest}, a powerful ensemble learning method that generates multiple decision trees and combines their outputs to improve prediction accuracy. This approach is particularly well-suited for computational chemistry due to its ability to handle large datasets, manage complex relationships between variables, and reduce overfitting. The Random Forest algorithm operates by constructing numerous random decision trees, each trained on different subsets of the dataset. The final prediction is obtained by averaging the outputs of all trees, ensuring robust and reliable results.

Moreover, the choice of the Random Forest algorithm is motivated by the presence of decision trees in various chemistry-related fields. In spectroscopy, for instance, decision trees are used in group theory to classify molecular symmetry. Similarly, in analytical chemistry, decision trees assist in substance separation techniques, while in organic chemistry, they are used to model reaction pathways.\par

This study aims to bridge the gap between artificial intelligence and computational chemistry, proving AI’s potential to revolutionise drug discovery and molecular research. The ability to predict inhibition potential with high accuracy can accelerate the development of new pharmaceuticals, reduce reliance on costly laboratory experiments, and contribute to a more efficient drug screening process. Furthermore, identifying key molecular descriptors correlated with inhibition could lead to a deeper understanding of chemical interactions, opening new avenues for research in medicinal chemistry and bioinformatics.
\newpage

\section{Objectives}

\section{Methodology}
The source code is all stored in the \href{https://github.com/SirSergi0/Repository---AI-application-for-azophotoswitches-optimization-with-pharmacological-interest}{\emph{AI application for azophotoswitches optimization with pharmacological interest} GitHub repository}\cite{GitHub}.

@@

\section{Results and Discussion}

@@

\begin{figure}[H]
\captionsetup{type=scheme}
\centering
\scalebox{0.8}{
\chemfig[angle increment=30]{
-[-1]S(=[-4]O)(=[-2]O)-[1]*6(-=-(-[1]*5(--O-(=[2.25]O)-(-[4.5]*6(-=-=-=))=))=-=)
}}
\caption{Chemical graph of Rofecoxib.}
\addcontentsline{lof}{figure}{Chemical graph of Rofecoxib.}
\label{RofecoxibFigure}
\end{figure}
\begin{definition}\label{definitionPersonCoefficient}
Pearson correlation coefficient: Given set of pairs of data $\{(x_i,y_i)\}_{i=1}^n$ the pearson correlation factor $r_{xy}$ is defined as,
\begin{align}
r_{xy}=\frac{\sum_{i=1}^n(x_i-\bar{x})(y_i-\bar{y})}{\sqrt{\sum_{i=1}^n(x_i-\bar{x}^2)}\sqrt{\sum_{i=1}^n(y_i-\bar{y}^2)}},
\end{align}
where $\bar{x}$ and $\bar{y}$ stand for the average value of ${x_i}_{i=1}^n$ and ${y_i}_{i=1}^n$ respectively. Note that $r_{xy}\in[-1,1]$. Therefore the sign of $r_{xy}$ is tightly related to the sign of alinear regression, more precisely if $x>0$, "$y$" generally\footnote{We would like to remark that the word "generally" stands for "the majority of the cases", since "generally" is commonly interpreted as a non-scientific/non-objective word} increases when "$x$" increases, as well as if $x<0$, "$y$" decreases when "$x$" increases.
\end{definition}
\begin{definition}\label{definitionTruePositiveRate}
True Positive Rate: quantity related to a Machine Learning Model's sensitivity defined as:
\begin{align}
\frac{TP}{TP+FN}
\end{align}
where $TP,FP,TN,FN$ stands for "True Positive", "False Positive", "True Negative" \& "False Negative" respectively.
\end{definition}

@@

>>>>

\setcounter{page}{1}
\pagenumbering{arabic}
\section{Introduction}
The impact of \gls{ai} on science has been nothing short of a groundbreaking revolution, with few comparable precedents. The rapid advancements in \gls{ai} have transformed numerous scientific fields\cite{AlphaFold2BiologyAndMedicine}\cite{NationalLibraryOfMedicineGeneralArticle}, including computational chemistry. Today, one of the primary goals of computational chemistry is to predict the properties of unstudied substances while minimizing experimental costs. Traditional approaches in chemistry often rely on complex laboratory techniques, which, while effective, can be time-consuming, expensive, and resource-intensive. In contrast, computational chemistry offers a wide range of methods capable of predicting a molecule’s properties with reasonable accuracy. However, when \gls{ai} comes into play, predictions have demonstrated an almost surgical precision.

Perhaps one of the most representative events showcasing the enormous impact of \gls{ai} on chemistry is the 2024 Nobel Prize in Chemistry. The winners, David Baker\cite{NobelPrizeBale}, along with Demis Hassabis and John Jumper\cite{NobelPrizeJumper}, were not traditionally trained chemists. Instead, their expertise lies in \gls{ai} algorithms and \gls{ml} methods applied to protein research. This milestone, among others, triggered a surge of chemistry researchers diving into the world of \gls{ai}, seeking applications for their respective fields. Today, the thrilling progress in computational chemistry has been further reinforced by these cutting-edge tools\cite{MachineLearningPaper5Lipoxygenase}, and the rapid pace of development keeps the scientific community eagerly anticipating future applications in fields such as medicine, materials science, and beyond. In this project we aim to apply the new AI and ML algorithms to our object of study, the \gls{ptgs2} also known as \gls{cox2}, a protein tightly linked to the onset of numerous cancers forms\cite{Cox2CancerReview}.

Although significant advancements have been made, cancer still accounts for over 8 million deaths per year worldwide, and the scientific and medical communities remain far from achieving its complete eradication. Inflammation is one of the hallmarks of carcinogenesis, in fact, various cancer therapies target inflammation as a means of preventing and reducing cancer occurrences. When a tissue is damaged, inflammation protects the organism from infections caused by external pathogens, a key function of the immune system to prevent the presence of invaders in the body. During the inflammatory process, cells proliferate under the command of the immune system to replace the damaged cells of the affected tissue. However, if this cell reproduction continues beyond the healing of the damaged tissue, it can potentially lead to cancer, contradicting the initial healing purpose of the inflammatory process. In some cases, inflammation can become chronic, leading to tumor development and uncontrolled cell proliferation. As a result, a wide range of drug prototypes have been designed to suppress inflammation. However, many of these drugs have been linked to severe side effects, including immunosuppression, cardiovascular risks, and gastrointestinal complications. Consequently, the administration of these drugs is often contrindicative, and the search for a more effective and safer treatment remains ongoing. Plently of the research in this field is mainly focused on the pro-inflamatory enzyme \gls{cox2}, one of the main commanders in the inflammation process and responsable to convert the arachidonic acid to prostaglandin \ch{H_2} (Scheme (\ref{Cox2MainReaction})). Subsequently, a therapy based on the chemical inhibition of the \gls{cox2} with no side effects has been one of the research lines in cancer treatment leading to a considerable amount of experiments and data.

\begin{figure}[H]
\captionsetup{type=scheme}
\centering
\schemestart
\scalebox{0.7}{
\chemname{\chemfig[angle increment=30, scale=0.1]{
HO-[1](=[3]O)-[-1]-[1]-[-1]-[1]=[-1]-[-3]-[-1]=[-3]-[7]-[-3]=[7]-[-7]-[7]=[-7]-[3]-[-7]-[7]-[-7]-[7]
}}{Arachidonic acid}
}
	\arrow{->[\gls{cox2}]}
\scalebox{0.7}{
\chemname{\chemfig[angle increment=30]{OH-[5](=[3]O)-[7]-[-3]-[7]-[-3]=[7]-[5]>:[7]*6(-(<[-3.8])-O-O-(<[3.8]C)-(<[-1]=[1]-[-1](<:[-3]OH)-[1]-[-1]-[1]-[-1]-[1])-)
}}{Prostaglandin \chemfig{H_2}}
}
\schemestop
\caption{Reaction catalysed by the COX-2 between arachidonic acid to prostaglandin H$_2$.}
\label{Cox2MainReaction}
\end{figure}

The increasing interest in \gls{cox2} inhibitors has granted the scientific community with an extensive database of molecular inhibition potentials for this protein. In this project, we focus on the Half Maximal Inhibitory Concentration (\gls{ic50}), a standard metric representing the concentration of a drug required to inhibit 50\% of a target protein’s activity. Related measures include \gls{ic90} and \gls{ic99}, which correspond to 90\% and 99\% inhibition, respectively. The lower the \gls{ic50} value of a molecule, the lower the concentration needed to inhibit \gls{cox2}, indicating higher efficiency. This factor is crucial in drug design, as a lower required dosage minimizes the presence of foreign substances in the body, thereby reducing the risk of adverse effects\footnote{Naturally, multiple other factors influence drug side effects.}.

Determining an experimental \gls{ic50} value can be both costly and time-consuming\footnote{Usually this parameter is computed throughout the Cheng Prusoff Equation (Def. (\ref{definitionChengPrusoff})) with experimental data.}. On the other hand, \gls{ai} provides an alternative by offering highly accurate predictions based on existing data, optimising research processes, and accelerating scientific discovery. In this scenario this project aims to implement artificial intelligence in computational chemistry, concretely, using \gls{ai}-based algorithms to predict a drug’s inhibition potential\cite{BookIC50} for a given protein with a relativelly good accuracy \footnote{The accuracy of the ML models is discussed on the Results and Discussion section (\ref{sectionResultsAndDiscussion}).}. To achieve this, we make use of the ChEMBL database\cite{ChemblDatabase}, a vast repository of bioactive molecules with drug-like properties. We extract all known molecular data with a documented inhibition potential for the target protein, creating a comprehensive dataset. The chemical descriptors of each molecule in the database are then computed using AlvaDesk\cite{MauriMolecularDescriptorsBook}\cite{AlvaDescSecondPaper} software. Around 5000 descriptors are calculated\cite{DescriptorsBook}, which comprehend from the elemental molecular weight to the complex equipotential electronic surface, providing critical information about each compound’s behaviour. The resulting dataset is subsequently used to train \gls{ai} models, enabling them to predict the inhibition potential of unknown compounds. Finally, we evaluate the reliability of each model by testing it against real experimental data.

It is important to emphasise the central hypothesis of this project: \emph{There exists a combination (or combinations) of chemical descriptors that are directly correlated with the inhibition of the protein}. While this idea may seem fundamental, it remains unproven due to the complexity of molecular interactions and the vast number of possible descriptor combinations. Despite significant progress in computational chemistry, identifying the exact descriptors that govern inhibition potential has been a persistent challenge. The lack of an ultimate proof underscores the need for advanced computational techniques. By analysing large datasets, \gls{ai} can detect hidden correlations that may not be immediately apparent through traditional statistical methods.

The \gls{ai} algorithm used is a in this study is a \gls{ml} model known as the \gls{rf} algorithm\cite{MachineLearningRandomForest}\cite{UAB_ComputationalChemistry}, a powerful ensemble learning method that generates multiple decision trees and combines their outputs to improve prediction accuracy. This approach is particularly well-suited for computational chemistry due to its ability to handle large datasets, manage complex relationships between variables, and reduce overfitting. The Random Forest algorithm operates by constructing numerous random decision trees, each trained on different subsets of the dataset. The final prediction is obtained by averaging the outputs of all trees, ensuring robust and reliable results.

Moreover, the choice of the Random Forest (\gls{rf}) algorithm is motivated by the presence of decision trees in various chemistry-related fields. In spectroscopy, for instance, decision trees are used in group theory to classify molecular symmetry. Similarly, in analytical chemistry, decision trees assist in substance separation techniques, while in organic chemistry, they are used to model reaction pathways.

By applying \gls{ai} models to \gls{cox2}, we assess their compatibility with the latest research findings\cite{Cox2InhibitorsReview}, demonstrating \gls{ai}’s potential as a powerful tool in computational chemistry research. Our approach not only validates \gls{ai}’s effectiveness in predicting inhibition potential but also provides insights into the underlying molecular mechanisms governing \gls{cox2} interactions.Additionaly, this study aims to bridge the gap between \gls{ai} and computational chemistry, reinforcing the \gls{ai}’s potential to revolutionise drug discovery and molecular research. The ability to predict inhibition potential with high accuracy can accelerate the development of new pharmaceuticals, reduce reliance on costly laboratory experiments, and contribute to a more efficient drug screening process. Furthermore, identifying key molecular descriptors correlated with inhibition could lead to a deeper understanding of chemical interactions, opening new avenues for research in medicinal chemistry and bioinformatics.

Currently, the pharmacological therapies for the \gls{cox2} inhibition are based on \gls{nsaid}\cite{nsaidDefinition} such as the popular ibuprofen or aspirin. However they have proved to be related to cardiovascular diseases and are contraindicated for people with more than 50 years or people with gastrointestinal problems, among others. One of the best drug candidates is the Celecoxib (Def. (\ref{definitionCelecoxib})) and the Rofecoxib (Def. (\ref{definitionRofecoxib})). The the Physical Chemistry Unit at UAB\cite{UAB_ComputationalChemistry}, is experimenting with azophotoswitches as COX-2 inhibitos.

\newpage
\section{Objectives}

\newpage
\section{Methodology}
The source code is all stored in the \href{https://github.com/SirSergi0/Repository---AI-application-for-azophotoswitches-optimization-with-pharmacological-interest}{\emph{AI application for azophotoswitches optimization with pharmacological interest} GitHub repository}\cite{GitHub}.

@@

\newpage
\section{Results and Discussion}\label{sectionResultsAndDiscussion}
In Figure (\ref{figureGraphicGbindingIC50}) we present the results bla bla bla the data is stored in appendix \ref{appendixTableOfResults}

\begin{figure}[H]
	\centering
	\includegraphics[width = \textwidth, trim={1.75cm 0.8cm 2.5cm 2cm}, clip]{../Plots/GbindingVSIC50.pdf}
	\caption{Graphic of the azophotoswitches from appendix \ref{appendixAzophotoshiches} where the x-axis represents the $\Delta G_{binding}$ and the y-axis the computed \gls{ic50}.}
	\label{figureGraphicGbindingIC50}
\end{figure}

@@

\begin{figure}[H]
\captionsetup{type=scheme}
\centering
\scalebox{0.8}{
\chemfig[angle increment=30]{
-[-1]S(=[-4]O)(=[-2]O)-[1]*6(-=-(-[1]*5(--O-(=[2.25]O)-(-[4.5]*6(-=-=-=))=))=-=)
}}
\caption{Chemical graph of Rofecoxib.}
\addcontentsline{lof}{figure}{Chemical graph of Rofecoxib.}
\label{RofecoxibFigure}
\end{figure}
\begin{definition}\label{definitionChengPrusoff}
Cheng Prusoff equation: standard equation used for the experimental computation of the IC50.
	\begin{align*}
		K_i=\frac{IC_{50}}{1+\frac{[S]}{K_m}}
	\end{align*}
\end{definition}
where $K_i$ is the binding affinity, $[S]$ is the substrate concentration, $K_m$ is the Michaelis constant and \gls{ic50} the half maximal inhibitory concentration.

\begin{definition}\label{definitionPersonCoefficient}
Pearson correlation coefficient: Given set of pairs of data $\{(x_i,y_i)\}_{i=1}^n$ the pearson correlation factor $r_{xy}$ is defined as,
\begin{align}
r_{xy}=\frac{\sum_{i=1}^n(x_i-\bar{x})(y_i-\bar{y})}{\sqrt{\sum_{i=1}^n(x_i-\bar{x}^2)}\sqrt{\sum_{i=1}^n(y_i-\bar{y}^2)}},
\end{align}
where $\bar{x}$ and $\bar{y}$ stand for the average value of ${x_i}_{i=1}^n$ and ${y_i}_{i=1}^n$ respectively. Note that $r_{xy}\in[-1,1]$. Therefore the sign of $r_{xy}$ is tightly related to the sign of alinear regression, more precisely if $x>0$, "$y$" generally\footnote{We would like to remark that the word "generally" stands for "the majority of the cases", since "generally" is commonly interpreted as a non-scientific/non-objective word} increases when "$x$" increases, as well as if $x<0$, "$y$" decreases when "$x$" increases.
\end{definition}
\begin{definition}\label{definitionTruePositiveRate}
True Positive Rate: quantity related to a Machine Learning Model's sensitivity defined as:
\begin{align}
\frac{TP}{TP+FN}
\end{align}
where $TP,FP,TN,FN$ stands for "True Positive", "False Positive", "True Negative" \& "False Negative" respectively.
\end{definition}

@@

\section{Table of results}\label{appendixTableOfResults}

\begin{table}[H]
    \centering
	\begin{tabular}{c|c|c|c|c|c|c}
		Type & Identifier & $R_1$ & $R_2$ & $R_3$ & $\Delta$ G$_{binding}$ & \gls{ic50} \\ \hline\hline
        Pyrazole & 1 & \ch{CF_3} & \ch{CH_2CH_3}& \ch{H} & -4.3505 & 145.893274 \\ \hline
        Pyrazole & 2 & \ch{CF_3} & \ch{CH_2CH_3}& \ch{F} & -3.619 & 160.715075 \\ \hline
        Pyrazole & 3 & \ch{CF_3} & \ch{CH_3} & \ch{F} & -0.5452 & 192.302751 \\ \hline
        Pyrazole & 4 & \ch{CF_3} & O\ch{CH_3} & \ch{H} & 9.9793 & 306.280176 \\ \hline
        Pyrazole & 5 & \ch{CF_3} & O\ch{CH_3} & \ch{F} & 1.5591 & 238.028688 \\ \hline
        Pyrazole & 6 & \ch{CF_3} & \ch{CH_3} & \ch{H} & -5.3292 & 142.842111 \\ \hline
        Pyrazole & 8 & \ch{F} & \ch{CH_3} & \ch{H} & 5.0694 & 240.476605 \\ \hline
        Pyrazole & 9 & \ch{Cl} & \ch{CH_3} & \ch{H} & -1.1579 & 171.543375 \\ \hline
        Pyrazole & 10 & \ch{Br} & \ch{CH_3} & \ch{H} & 6.3225 & 247.718353 \\ \hline
        Pyrazole & 11 & \ch{CH_3} & \ch{CH_3} & \ch{H} & 3.0677 & 215.242455 \\ \hline
        Pyrazole & 12 & \ch{H} & \ch{CH_3} & \ch{F} & 1.0334 & 196.189309 \\ \hline
        Pyrazole & 13 & \ch{F} & \ch{CH_3} & \ch{F} & 3.2216 & 220.685948 \\ \hline
        Pyrazole & 14 & \ch{Cl} & \ch{CH_3} & \ch{F} & 5.1623 & 231.70988 \\ \hline
        Pyrazole & 15 & \ch{Br} & \ch{CH_3} & \ch{F} & 5.6163 & 235.929591 \\ \hline
        Pyrazole & 16 & \ch{CH_3} & \ch{CH_3} & \ch{F} & -3.3079 & 149.258659 \\ \hline
        Furan & 1 & \ch{CF_3} & \ch{H} &  & -0.9611 & 171.3118 \\ \hline
        Furan & 2 & \ch{H} & \ch{H} &  & 0.193 & 189.723234 \\ \hline
        Furan & 3 & \ch{F} & \ch{H} &  & -4.8383 & 133.666586 \\ \hline
        Furan & 4 & \ch{Cl} & \ch{H} &  & -2.4267 & 158.679542 \\ \hline
        Furan & 5 & \ch{Br} & \ch{H} &  & -3.4217 & 144.849203 \\ \hline
        Furan & 6 & \ch{CH_3} & \ch{H} &  & -3.9711 & 139.974502 \\ \hline
        Furan & 7 & \ch{CF_3} & \ch{F} &  & -5.4022 & 148.510406 \\ \hline
        Furan & 8 & \ch{H} & \ch{F} &  & -6.55 & 122.352426 \\ \hline
        Furan & 9 & \ch{F} & F &  & -0.1311 & 189.013485 \\ \hline
        Furan & 10 & \ch{Cl} & \ch{F} &  & -5.8185 & 127.541229 \\ \hline
        Furan & 11 & \ch{Br} & \ch{F} &  & 6.1474 & 241.164891 
            \end{tabular}
\end{table}

\begin{table}[H]
    \centering
	\begin{tabular}{c|c|c|c|c|c|c}
		Type & Identifier & $R_1$ & $R_2$ & $R_3$ & $\Delta$ G$_{binding}$ & \gls{ic50} \\ \hline\hline
        Thiophene & 1 & \ch{F} & \ch{H} &  & 1.2724 & 192.519195 \\ \hline
        Thiophene & 2 & \ch{H} & \ch{F} &  & -2.7842 & 152.750403 \\ \hline
        Thiophene & 3 & \ch{Cl} & \ch{F} &  & -5.7964 & 120.103107 \\ \hline
        Pyrrole & 1 & \ch{CF_3} & \ch{CH_3} & \ch{H} & -3.5279 & 151.424098 \\ \hline
        Pyrrole & 2 & \ch{Cl} & \ch{CH_3} & \ch{F} & -1.3499 & 164.211081 \\ \hline
        Benzene & 1 & \ch{CF_3} & \ch{CH_2CH_3}&  & -1.339 & 168.708238 \\ \hline
        Benzene & 2 & \ch{CF_3} & \ch{NCH_3COCH_3} &  & -1.9922 & 208.784609 \\ \hline
        Benzene & 3 & \ch{CF_3} & \ch{NHCH_3} &  & 4.8759 & 232.955871 \\ \hline
        Benzene & 4 & \ch{CF_3} & \ch{OCH_3} &  & -3.4432 & 155.416193 \\ \hline
        Indole & 1 & \ch{H} &  &  & -9.7543 & 74.9840521 \\ \hline
        Indole & 1 & \ch{H} &  &  & -9.7543 & 74.9840521 \\ \hline
        Indole & 2 & \ch{F} &  &  & -6.3397 & 108.725159 \\ \hline
        Indole & 2 & \ch{F} &  &  & -6.3397 & 108.725159 \\ \hline
        Indole & 3 &  &  &  & -5.532 & 111.153348 \\ \hline
        TwoRings & 2 & \ch{NH} & O & \ch{H} & -2.2146 & 165.648426 \\ \hline
        TwoRings & 3 & O & \ch{NH} & \ch{H} & -0.7334 & 178.354687 \\ \hline
        TwoRings & 6 & \ch{NH} & O & \ch{CH_3} & 5.5592 & 235.15246 \\ \hline
        TwoRings & 7 & O & \ch{NH} & \ch{CH_3} & -10.6712 & 77.7978863 \\ \hline
        TwoRings & 8 & O & O & \ch{CH_3} & -3.5413 & 142.268104 
    \end{tabular}
\end{table}
